Technical Report

### 2018-06-05 fully-abstract-comp/technical-report.tex
Discharge some simple proofs.
Start on proof of compatibility of initial configuration.

\begin{mathpar}
  \inference{
    \var{comp}_1 = (\mscode[1], \msdata[1], \overline{c_{\mathrm{import},1}}, \overline{c_{\mathrm{export},1}}, \sigrets[1], \sigcloss[1],A_{\linear,1})\\
    \var{comp}_2 = (\mscode[2], \msdata[2], \overline{c_{\mathrm{import},2}}, \overline{c_{\mathrm{export},2}}, \sigrets[2], \sigcloss[2],A_{\linear,2})\\
    \var{comp}_3 = (\mscode[3], \msdata[3], \overline{c_{\mathrm{import},3}}, \overline{c_{\mathrm{export},3}}, \sigrets[3], \sigcloss[3],A_{\linear,3})\\
    \mscode[3] = \mscode[1] \uplus \mscode[2] &
    \msdata[3] = \msdata[1] \uplus \msdata[2] \\
    \overline{c_{\mathrm{export},3}} = \overline{c_{\mathrm{export},1}} \cup \overline{c_{\mathrm{export},2}}&
    \overline{c_{\mathrm{import},3}} = (\overline{c_{\mathrm{import},1}} \cup \overline{c_{\mathrm{import},2}}) \setminus \overline{c_{\mathrm{export},3}}\\
    \sigrets[3] = \sigrets[1] \uplus \sigrets[2] &
    \sigcloss[3] = \sigcloss[1] \uplus \sigcloss[2] &
    A_{\linear,3} = A_{\linear,1} \uplus A_{\linear,2}
  } {
    \var{comp}_3 = \var{comp}_1 \bowtie \var{comp}_2
  }
  \and
  \inference{
    \var{comp}_0'' = \var{comp}_0 \bowtie \var{comp}_0'
  }{
    (\var{comp}_0'',c_{\mathrm{main},c}, c_{\mathrm{main},d}) = \var{comp}_0 \bowtie (\var{comp}_0',c_{\mathrm{main},c}, c_{\mathrm{main},d})
  }
  \and
  \inference{
    \var{comp}_0'' = \var{comp}_0 \bowtie \var{comp}_0'
  }{
    (\var{comp}_0'',c_{\mathrm{main},c}, c_{\mathrm{main},d}) = (\var{comp}_0,c_{\mathrm{main},c}, c_{\mathrm{main},d}) \bowtie \var{comp}_0'
  }
\end{mathpar}

\begin{lemma}[Linking preserves component well-formedness]
  \label{lem:linking-well-formedness}
  If $\vdash \var{comp}_1$ and $\vdash \var{comp}_2$, then $\vdash \var{comp}_1 \bowtie \var{comp}_2$.
\end{lemma}
\begin{proof}
  TODO
\end{proof}

@@

\begin{lemma}
  $\oplus$ is associative and commutative.
\end{lemma}
\begin{proof}
  TODO
\end{proof}

@@

\begin{lemma}[Compatibility lemma for initial execution configuration construction]
  If
  \begin{itemize}
  \item $\npair{\stpair{\var{comp}}{\var{comp}}} \in \lrcomp(W)$
  \item $\var{comp}_S\rightsquigarrow \Phi_S$
  \item $\var{comp}_T \rightsquigarrow \Phi_T$,
  \end{itemize}
  then
  \begin{itemize}
  \item $\npair{\stpair{\Phi}{\Phi}}\in\lrec(W)$
  \end{itemize}
\end{lemma}

>>>>

\begin{mathpar}
  \inference{
    \var{comp}_1 = (\mscode[1], \msdata[1], \overline{c_{\mathrm{import},1}}, \overline{c_{\mathrm{export},1}}, \sigrets[1], \sigcloss[1],A_{\linear,1})\\
    \var{comp}_2 = (\mscode[2], \msdata[2], \overline{c_{\mathrm{import},2}}, \overline{c_{\mathrm{export},2}}, \sigrets[2], \sigcloss[2],A_{\linear,2})\\
    \var{comp}_3 = (\mscode[3], \msdata[3], \overline{c_{\mathrm{import},3}}, \overline{c_{\mathrm{export},3}}, \sigrets[3], \sigcloss[3],A_{\linear,3})\\
    \mscode[3] = \mscode[1] \uplus \mscode[2] &
    \msdata[3] = \msdata[1] \uplus \msdata[2] \\
    \overline{c_{\mathrm{export},3}} = \overline{c_{\mathrm{export},1}} \cup \overline{c_{\mathrm{export},2}}&
    \overline{c_{\mathrm{import},3}} = (\overline{c_{\mathrm{import},1}} \cup \overline{c_{\mathrm{import},2}}) \setminus \overline{c_{\mathrm{export},3}}\\
    \sigrets[3] = \sigrets[1] \uplus \sigrets[2] &
    \sigcloss[3] = \sigcloss[1] \uplus \sigcloss[2] &
    A_{\linear,3} = A_{\linear,1} \uplus A_{\linear,2}\\
    \dom(\mscode[3]) \mathrel{\#} \dom(\msdata[3]) & \sigrets[3] \mathrel{\#} \sigcloss[3]\\
  } {
    \var{comp}_3 = \var{comp}_1 \bowtie \var{comp}_2
  }
  \and
  \inference{
    \var{comp}_0'' = \var{comp}_0 \bowtie \var{comp}_0'
  }{
    (\var{comp}_0'',c_{\mathrm{main},c}, c_{\mathrm{main},d}) = \var{comp}_0 \bowtie (\var{comp}_0',c_{\mathrm{main},c}, c_{\mathrm{main},d})
  }
  \and
  \inference{
    \var{comp}_0'' = \var{comp}_0 \bowtie \var{comp}_0'
  }{
    (\var{comp}_0'',c_{\mathrm{main},c}, c_{\mathrm{main},d}) = (\var{comp}_0,c_{\mathrm{main},c}, c_{\mathrm{main},d}) \bowtie \var{comp}_0'
  }
\end{mathpar}

\begin{lemma}[Linking preserves component well-formedness]
  \label{lem:linking-well-formedness}
  If $\vdash \var{comp}_1$ and $\vdash \var{comp}_2$, then $\vdash \var{comp}_1 \bowtie \var{comp}_2$.
\end{lemma}
\begin{proof}
  Follows by induction on the component validity judgement and definition-chasing.
  The most interesting point is related to imports that are resolved from the other component during linking, but we know that those exports satisfy the $\mathrm{comp-value}$ judgement.
\end{proof}

@@

\begin{lemma}
  $\oplus$ is associative and commutative.
\end{lemma}
\begin{proof}
  Follows easily from the definitions.
\end{proof}

@@

\begin{lemma}[Compatibility lemma for initial execution configuration construction]
  If
  \begin{itemize}
  \item $\npair{\stpair{\var{comp}}{\var{comp}}} \in \lrcomp(W)$
  \item $\var{comp} \rightsquigarrow \Phi$,
  \item TODO: no stack regions yet?
  \end{itemize}
  then $\exists W' \future W$ such that
  \begin{itemize}
  \item $\npair{\stpair{\Phi}{\Phi}}\in\lrec(W')$
  \end{itemize}
\end{lemma}
\begin{proof}
  Take $\var{comp} = ((\mscode, \msdata, \overline{c_{\mathrm{import}}}, \overline{c_{\mathrm{export}}}, \sigrets, \sigcloss,A_\linear),  c_{\mathrm{main},c}, c_{\mathrm{main},d})$.
  Then we know from $\var{comp} \rightsquigarrow \Phi$ that
  \begin{itemize}
  \item $\reg(\pcreg) = c_{\mathrm{main},c}$
  \item $\reg(\rdata) = c_{\mathrm{main},d}$ 
  \item $\src{\reg(\rstk) = \stkptr{\rx,\baddr_\stk,\eaddr_\stk,\eaddr_\stk}}$ 
  \item $\trg{\reg(\rstk) = ((\rx,\linear),\baddr_\stk,\eaddr_\stk,\eaddr_\stk)}$ 
  \item $\reg(\RegName \setminus \{\pcreg,\rdata,\rstk\}) = 0$
  \item $\range{\ms_\stk} = \{0\}$
  \item $\mem = \mscode \uplus \msdata \trg{\;\uplus\; \ms_\stk}$
  \item $[\baddr_\stk,\eaddr_\stk] = \dom(\ms_\stk ) \mathrel{\#} (\dom(\mscode) \cup \dom(\msdata))$
  \item $\overline{c_{\mathrm{import}}} = \emptyset$
  \end{itemize}

  From $\npair{\stpair{\var{comp}}{\var{comp}}} \in \lrcomp(W)$, we know that
  $\{c_{\mathrm{main},c}, c_{\mathrm{main},d}\}\subseteq \overline{c_{\mathrm{export}}}$ and 
  $\npair{(\var{comp}_0,\var{comp}_0)} \in \lrcomp(W)$ with $\var{comp}_0 = (\mscode, \msdata, \overline{c_{\mathrm{import}}}, \overline{c_{\mathrm{export}}}, \sigrets, \sigcloss,A_\linear)$.
  From this, it follows that $W \vdash \var{comp}$ and for all  $W' \future W$, if
  \begin{equation*}
    \overline{\npair[n']{(c_{\mathrm{import}},c_{\mathrm{import}})}} \in \lrv(\purePart{W'}) \text{ for all $n' < n$}
  \end{equation*}
  then
  \begin{equation*}
    \overline{\npair{(c_{\mathrm{export}},c_{\mathrm{export}})}} \in \lrv(\purePart{W'})
  \end{equation*}
  Since $\overline{c_{\mathrm{import}}} = \emptyset$, the former holds vacuously and the latter follows for every $W' \future W$.

  Now take $\overline{r_a} \not\in\dom(\pwfree)$ and 
  \begin{align*}
    W' &= W\overline{\update{\mathrm{free}(r_a)}{\stdreg{\{a\},\gc}{\pur}}}_{a \in [\baddr_\stk,\eaddr_\stk]}\\
   W_\pcreg &= \purePart{W'}\\
    W_R &= \purePart{W}\overline{\update{\mathrm{free}(r_a)}{\stdreg{\{a\},\gc}{\spatialo}}}_{a \in [\baddr_\stk,\eaddr_\stk]}\\
    W_M &= W\overline{\update{\mathrm{free}(r_a)}{\stdreg{\{a\},\gc}{\spatial}}}_{a \in [\baddr_\stk,\eaddr_\stk]}
  \end{align*}
  Then $W' = W_M \oplus W_R \oplus W_\pcreg$ and by definition of $\lrec$, it suffices to prove that 
  \begin{itemize}
  \item $\reg_S(\pcreg) = ((\rx,\lin),\baddr,\eaddr,\aaddr)$:
    TODO
  \item $(\trust = \trusted \text{ iff } \aaddr \in \ta)$:
    TODO
  \item $\npair{( \reg_S(\pcreg),\reg_T(\pcreg) )} \in \lrvg{\trust}(W_\pcreg)$:
    TODO
  \item $\memSat{\ms_S,\ms_\stk,\stk,\ms_T}{W_M}$:
    TODO
  \item $\npair{\stpair{\reg}{\reg}} \in \lrrg{\trust}(W_R)$:
    TODO
  \end{itemize}

\end{proof}
